Predicting Remaining Useful Life of NASA Aircraft Engines

### 2025-02-19 index.qmd
Dataset link added

<!-- -->

>>>>

We will be using the test_FD002 and train_FD002 datasets available for download at
[NASA's Open Data Portal](https://data.nasa.gov/Aerospace/CMAPSS-Jet-Engine-Simulated-Data/ff5v-kuh6/about_data) and also avaialble on the home page of our [GitHub repository](https://github.com/JR-87/capstone4ds_reed).

```{r}
testurl <- 'https://raw.githubusercontent.com/JR-87/capstone4ds_reed/refs/heads/main/test_FD002.txt'

test <- read.table(testurl, header = TRUE, sep = '')
head(test)
```
```{r}
trainurl <- 'https://raw.githubusercontent.com/JR-87/capstone4ds_reed/refs/heads/main/train_FD002.txt'

test <- read.table(trainurl, header = TRUE, sep = '')
head(test)
```
